\chapter*{Foreword}
\addcontentsline{toc}{chapter}{Foreword}

\newthought{This masters's thesis} is part of my 4+4 Ph.D. project (also known as an integrated Ph.D.). In my Ph.D. I study the use of machine learning and deep learning in the field of ancient genomics. In this field ancient DNA is sampled and analysed with the hope of finding patterns and structure in the genome, patterns that were previously unknown. The overall goal is two-fold. On the big scale it is to better understand human history in the broadest sense of the word history. Where did we come from, where did we go? On a much smaller scale, the goal is to understand local history and migration patterns; how did we end up where we did? 

It is with this background that this project should be seen: as an introduction to the general use of applied machine learning. Since I continue with my Ph.D. after this project, the focus has been on learning and developing methods and tools which will be useful in the latter part of the Ph.D. The master's project originally started in early \num{2017} and became part of the Ph.D. project in the autumn of the same year. 

I would like to thank my supervisor Troels Petersen for his help and time during the project, but most of all for his enthusiasm. I look forward to the continued collaboration during my Ph.D. I would also like to thank the office colleagues, both previous ones such as Stefan Hasselgren, Benjamin Henckel, Frederik Faye, and Helle Gormsen, but also current ones as Helle Leerberg. A special thank goes to Daniel Nielsen for fruitful discussions and general technical help during the recent three years and for letting me lighten our office. I would also like to thank Boligsiden for all their help providing data and valuable insights during the first part of this project. Finally I would like to thank my friends and family for the continued support during this project and hopefully the rest of my Ph.D. 